### 2022-02-18 sections/introduction.tex
updates tables

In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small $\BR(t\to qH)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM.
%The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}. 
%Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
%Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
%has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
%and excellent diphoton mass re\-so\-lu\-tion. 
%Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
%are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
%are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
%and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
%Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
%of $\BR(H\to b\bar{b})\simeq 58\%$.
Compared to Run~1, the Run~2 searches benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton (electron or muon) signatures resulting from 
$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
%The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.

@@

>>>>

In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small $\BR(t\to qH)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM.
%The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}. 
%Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
%Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
%has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
%and excellent diphoton mass re\-so\-lu\-tion. 
%Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
%are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
%are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
%and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
%Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
%of $\BR(H\to b\bar{b})\simeq 58\%$.
Compared to Run~1, the Run~2 searches(~\ref{tab:limits_summary}) benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton (electron or muon) signatures resulting from 
$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
%The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.

@@

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$.}}
\begin{center}
\begin{tabular}{lcc}
\toprule\toprule
 & \multicolumn{1}{c}{95\% CL upper observed limits} & \multicolumn{1}{c}{95\% CL observed upper limits}  \\
 & \multicolumn{1}{c}{on $\BR(t \to Hc)$} & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
\midrule\midrule
ATLAS $H \to b\bar{b}$~\cite{fcnc36} & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
ATLAS $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36} & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
ATLAS $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob}  & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$  \\ 
ATLAS $H \to \gamma\gamma$~\cite{Aaboud:2017mfd} & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
CMS   $H\to b\bar{b}$~\cite{Sirunyan:2017uae} & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
\midrule
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary}
\end{center}
\end{table}

### 2022-02-18 sections/strategy_Htautau.tex
updates tables

%%%%%%%%%%%%%%%
\begin{table*}[t!]
  \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
      The values in percent (\%) represent the separation and importance of each variable.
    The descriptions of each variable are provided in the following text.}}
\label{tab:importance_xTFW}
\input{tables/xTFW_Merged}
\end{table*}

\begin{table*}[t!]
  \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
      The values in percent (\%) represent the separation and importance of each variable.
    The descriptions of each variable are provided in the following text.}}
\label{tab:importance_tthML}
\input{tables/tthML_Merged}
\end{table*}

@@

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_xTFW} and~\ref{tab:importance_tthML}. The discriminating variables used are:

>>>>

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Discriminating variables used in the training of the BDT. The values represent the importance rankings of each variable and cross($\times$) denotes the variable is not used in the training. The descriptions of each variable are provided in the following text.}}
\label{tab:importance}
 \centering
 \begin{tabular}{cccccccc} \toprule\toprule
& $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l\thadhad$     & $t_h\thadhad$-2j & $t_h\thadhad$-3j       \\\midrule 
 $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
 $\chi^{2}$                                          & $\times$  &  $\times$           &  $\times$         & $14$     & $\times$      & $\times$ & $\times$      \\
 \text{max}($\eta_{\tau}$)                           & $4$       &  $\times$           &  $4$              & $\times$ & $10$          & $\times$ & $\times$       \\
 $m^{\text{T}}_{\text{W}}$                           & $10$      &  $\times$           &  $8$              & $\times$ & $13$          & $\times$ & $\times$        \\
 $m_{\tau,\tau}$                                     & $\times$  &  $2$                &  $\times$         & $3$      & $\times$      & $1$      & $1$          \\
 $m_{\text{t},\text{SM}}$                            & $\times$  &  $1$                &  $\times$         & $2$      & $\times$      & $3$      & $4$          \\
 $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     & $\times$      & $\times$ & $\times$        \\
 $m_{\text{t},\text{FCNC}}$                          &  $\times$ &  $\times$           &  $\times$         & $\times$ & $\times$      & $10$     & $6$\\
 $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &  $\times$           &  $5$              & $\times$ & $4$           & $\times$ & $\times$        \\
 $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
 $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
 $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
 $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  & $\times$  &  $10$               &  $\times$         & $12$     & $\times$      & $8$    & $8$          \\
 $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  & $\times$  &  $7$                &  $\times$         & $4$      & $\times$      & $9$    & $11$         \\
 $P_{\text{T,\tauhadvis}} $                          & $\times$  &  $\times$           &  $\times$         & $\times$ & $9$           & $\times$ & $\times$        \\
 $m_{\text{t},\text{FCNC},\text{vis}}$               & $\times$  &  $\times$           &  $\times$         & $\times$ & $3$           & $\times$ & $\times$       \\
 $\Delta\phi(\tau\tau,\met)$                         & $\times$  &  $6$    			   &  $\times$         & $16$     & $\times$      & $13$   & $12$         \\
 $\met\text{centrality}$                             & $\times$  &  $13$               &  $\times$         & $15$     & $\times$      & $12$   & $9$         \\
 \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &  $\times$           &  $3$              & $\times$ & $14$          & $\times$ & $\times$        \\
 $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          & $\times$ & $\times$        \\
 $\Delta R(\tau,\tau)$                               & $\times$  &  $\times$           &  $\times$         & $\times$ & $2$           & $4$    & $3$             \\
 $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          & $\times$ & $\times$        \\
 $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          & $\times$ & $\times$       \\
 $\Delta R(\ell+\text{b-jet},\tau\tau )$             & $\times$  &  $\times$           &  $\times$         & $\times$ & $7$           & $\times$ & $\times$        \\
 $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
 \text{Min}($m_{\text{light-jet},\text{light-jet}}$) & $\times$  &  $12$               &  $\times$         & $11$     & $\times$      & $\times$ & $\times$        \\
 \bottomrule\bottomrule\\
 \end{tabular}
\end{table*}

%%%%%%%%%%%%%%%
%%%  \begin{table*}[t!]
%%%    \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
%%%        The values in percent (\%) represent the separation and importance of each variable.
%%%      The descriptions of each variable are provided in the following text.}}
%%%  \label{tab:importance_xTFW}
%%%  \input{tables/xTFW_Merged}
%%%  \end{table*}
%%%  
%%%  \begin{table*}[t!]
%%%    \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
%%%        The values in percent (\%) represent the separation and importance of each variable.
%%%      The descriptions of each variable are provided in the following text.}}
%%%  \label{tab:importance_tthML}
%%%  \input{tables/tthML_Merged}
%%%  \end{table*}

@@

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance}. The discriminating variables used are:

### 2022-02-18 sections/systematic_uncertainties.tex
updates tables

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel. The uncertainties are symmetrised for presentation and grouped into the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
$\text{Fake modelling} $   & $13.5$ \\
$\text{Instrument}     $   & $2.6$  \\
$\text{Jets}           $   & $1.7$   \\
$\text{Met}            $   & $0.4$   \\
$\tau                  $   & $7.2$    \\
$\text{b-tagging}       $  & $0.3$    \\
$\text{Signal Theory}  $   & $1.5$   \\
$\text{Other MC theory} $  & $2.7$    \\
$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
$\text{Statistics}      $  & $11.2$   \\
$\text{Total systematic}$  & $24.2$  \\ \midrule
$\text{Total}  $           & $26.7$ \\
\bottomrule\bottomrule
\end{tabular}
\label{tab:had_sys_impact}
\end{table}

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel. The uncertainties are symmetrised for presentation and grouped into  the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
$\text{Fake modelling}     $ & $       2.1             $\\
$\text{Instrument}         $ & $       0.7             $\\
$\text{Jets}               $ & $       2.8             $\\
$\text{Met}                $ & $       1.2             $\\
$\text{Lepton}             $ & $       0.7             $\\
$\tau                      $ & $       2.3             $\\
$\text{b-tagging}          $ & $       4.8             $\\
$\text{Signal Theory}      $ & $       6.9             $\\
$\text{Other MC theory}    $ & $       2.1             $\\
$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
$\text{Statistics}         $ & $       5.9             $\\
$\text{Total systematic}   $ & $       12.9            $\\\midrule
$\text{Total}              $ & $       14.2            $\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:lep_sys_impact}
\end{table}

>>>>

\begin{table}[h!]
\caption{List of relative uncertainties of the signal strength from the combined fit. The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
\label{tab:had_sys_impact}
\begin{center}
\begin{tabular}{%
@{}l%
S%
S%
@{}%
}
\toprule
\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\mu/\mu [\%]$} \\
                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
Lepton                                  & 0.6           &1.0         \\
Met                                     & 0.7           &0.8         \\
Luminosity and Pileup                   & 1.0           &1.3         \\
Theoretical uncertainty in other MC     & 2.1           &2.9         \\
Jets                                    & 2.4           &3.2         \\
Flavour tagging                         & 2.7           &3.7         \\
Misidentified $\tau$                    & 3.4           &4.8         \\
Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
Hadronic $\tau$ decays                  & 3.3           &4.4         \\
Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
Total statistics uncertainty            & 5.1           &7.0         \\
Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
Total                                   & 12.3          &16.9        \\
\bottomrule
\end{tabular} 
\end{center}
\end{table}

%% Fake method    0.0476721  ( +0.0476721, -0.0476721 )
%% FullSyst    0.154686  ( +0.154686, -0.154686 )
%% Gammas    0.0700708  ( +0.0700708, -0.0700708 )
%% Instrument    0.0131647  ( +0.0131647, -0.0131647 )
%% JET    0.0320897  ( +0.0320897, -0.0320897 )
%% Lepton    0.0104552  ( +0.0104552, -0.0104552 )
%% MET    0.00841447  ( +0.00841447, -0.00841447 )
%% SignalTheory    0.0699833  ( +0.0699833, -0.0699833 )
%% TAU    0.0437292  ( +0.0437292, -0.0437292 )
%% Theory    0.029182  ( +0.029182, -0.029182 )
%% btag    0.0367613  ( +0.0367613, -0.0367613 )
%% ttbarTheory    0.0427391  ( +0.0427391, -0.0427391 )

%% Fake method   0.0341326  ( +0.0341326, -0.0341326 )
%% FullSyst      0.112111      ( +0.112111, -0.112111 )
%% Gammas        0.0509968       ( +0.0509968, -0.0509968 )
%% Instrument    0.0093934  ( +0.0093934, -0.0093934 )
%% JET           0.0235705  ( +0.0235705, -0.0235705 )
%% Lepton        0.00568277  ( +0.00568277, -0.00568277 )
%% MET           0.00704844  ( +0.00704844, -0.00704844 )
%% SignalTheory  0.0526104  ( +0.0526104, -0.0526104 )
%% TAU           0.032714  ( +0.032714, -0.032714 )
%% Theory        0.0210686  ( +0.0210686, -0.0210686 )
%% btag          0.027376  ( +0.027376, -0.027376 )
%% ttbarTheory   0.0289194  ( +0.0289194, -0.0289194 )

%\begin{table}[htbp]
%\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel. The uncertainties are symmetrised for presentation and %grouped into the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations %introduced by the fit
%}
%\small
%\centering
%\begin{tabular}{cc} \toprule\toprule
%$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
%$\text{Fake modelling} $   & $13.5$ \\
%$\text{Instrument}     $   & $2.6$  \\
%$\text{Jets}           $   & $1.7$   \\
%$\text{Met}            $   & $0.4$   \\
%$\tau                  $   & $7.2$    \\
%$\text{b-tagging}       $  & $0.3$    \\
%$\text{Signal Theory}  $   & $1.5$   \\
%$\text{Other MC theory} $  & $2.7$    \\
%$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
%$\text{Statistics}      $  & $11.2$   \\
%$\text{Total systematic}$  & $24.2$  \\ \midrule
%$\text{Total}  $           & $26.7$ \\
%\bottomrule\bottomrule
%\end{tabular}
%\label{tab:had_sys_impact}
%\end{table}

%\begin{table}[htbp]
%\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel. The uncertainties are symmetrised for presentation and %grouped into  the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations %introduced by the fit
%}
%\small
%\centering
%\begin{tabular}{cc} \toprule\toprule
%$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
%$\text{Fake modelling}     $ & $       2.1             $\\
%$\text{Instrument}         $ & $       0.7             $\\
%$\text{Jets}               $ & $       2.8             $\\
%$\text{Met}                $ & $       1.2             $\\
%$\text{Lepton}             $ & $       0.7             $\\
%$\tau                      $ & $       2.3             $\\
%$\text{b-tagging}          $ & $       4.8             $\\
%$\text{Signal Theory}      $ & $       6.9             $\\
%$\text{Other MC theory}    $ & $       2.1             $\\
%$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
%$\text{Statistics}         $ & $       5.9             $\\
%$\text{Total systematic}   $ & $       12.9            $\\\midrule
%$\text{Total}              $ & $       14.2            $\\
%\bottomrule\bottomrule
%\end{tabular}
%\label{tab:lep_sys_impact}
%\end{table}
